---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
activity <- read.csv("activity.csv")
activity$date <- as.Date(activity$date, format='%Y-%m-%d')
```

## What is mean total number of steps taken per day?
#### 1.Make a histogram of the total number of steps taken each day
```{r}
totalstepsperday <- aggregate(activity$steps~activity$date,activity,sum)
colnames(totalstepsperday) <- c("Date", "Steps")
hist(totalstepsperday$Steps, xlab = "Total Steps Per Day", main = "Total Steps Per Day Histogram")
```


#### 2.Calculate and report the mean and median total number of steps taken per day
```{r}
mean(totalstepsperday$Steps)
median(totalstepsperday$Steps)
```

## What is the average daily activity pattern?
#### 1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
tspinterval <- aggregate(activity$steps~activity$interval,activity,mean)
colnames(tspinterval) <- c("Interval", "Steps")
plot(tspinterval$Interval,tspinterval$Steps,type = "l", xlab = "Time Interval", ylab = "Average Steps", main = "Average Steps By Interval Across All Days")
```

####2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
maxsteps <- which.max(tspinterval$Steps)
tspinterval$Interval[maxsteps]
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
